The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-06-05 Paper/jaccardbaetica.tex
fix bug

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue)}
\label{frequency}
\end{figure} 
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

explicar las razones del conventus no?
AQUÍ QUIZÁS HABLAR DE SELLOS NO?

@@

\subsection{Quantifying the diversity Dissimilarity correlation}

@@

The results of the case study could be interpreted due to several reason according to previous hypotheses. On the one hand, the use of these amphoric stamps could have been exclusively running by the owner or owners of the workshop to distinguish the amphora workshop (CITAR). This hypotheses would explain the fact that we do not find similar stamps in different workshops, however, we found different amphora stamps in a same workshops that they would be barely difficult to assign different owners. Neither a kind of quality distinction does seem to be used to specify the quality or value of the product \citep{callender}. On the other hand, it can be interpreted somehow a batch systematic organization. Considering that Dressel 20 was not marked in several cases, some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped \citep{berni_millet_epigrafianforica_2008}. This method would be used as an identifier to count the number of amphorae of a branch (CITAR). This it could be explain wherefore we found different stamps in a same workshop. 
In any case, we do not have enough archaeological evidence that can validate the interpretations presented here and our results are certainly valid only with the context of our case study.

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon and Nachete. 
All data has been analysed and conducted in R program version 3.2.4, using the packages \textit{vegan} \citep{oksanen_vegan_2007}.

>>>>

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue).}
\label{frequency}
\end{figure} 
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

%explicar las razones del conventus no?
%aquí hablar de sellos?

@@

\subsection{Quantifying the diversity}

@@

The results of the case study could be interpreted due to several reason according to previous hypotheses. On the one hand, the use of these amphoric stamps could have been exclusively running by the owner or owners of the workshop to distinguish the amphora workshop (CITAR). This hypotheses would explain the fact that we do not find similar stamps in different workshops, however, we found different amphora stamps in a same workshops that they would be barely difficult to assign different owners. Neither a kind of quality distinction does seem to be used to specify the quality or value of the product \citep{callender}. On the other hand, it can be interpreted somehow a batch systematic organization. Considering that Dressel 20 was not marked in several cases, some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped \citep{berni_millet_epigrafianforica_2008}. This method would be used as an identifier to count the number of amphorae of a branch (CITAR). This method could also have served to identify different groups of potter workers working in the same amphora workshop. Potters could have marked the amphorae to distinguish  different groups working in parallel \citep{li_crossbows_2014}. This it could be explain wherefore we found different stamps in a same workshop. 
In any case, we do not have enough archaeological evidence that can validate the interpretations presented here and our results are certainly valid only with the context of our case study.

@@

The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon, Juan Moros and Ignacio Morer for their useful suggestions.  
All data has been analysed and conducted in R program version 3.2.4, using the packages \textit{vegan} \citep{oksanen_vegan_2007}, \textit{ggplot2} \citep{ggplot2:_2016}. Source and code are available
